Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/simple-regret.tex
Added explanation of Algorithm 1

>>>>

To identify a high-reward intervention, Algorithm~\ref{alg:simple} break $T$ rounds into halves. 
In the first half, the non-interventional action $do()$ is played and the rewards observed.
These are used to estimate the occurrance probabilities $\vec{q}$ and the value of $m(\vec{q})$.
The remainder of the rounds are then evenly split to estimate the infrequently observed interventions, as determined by the estimate for $m(\vec{q})$.
Although very simple, the following two theorems show that this algorithm is effectively optimal.
